Hunting the Parent of the Orphan Stream: Identifying Stream Members \\ from Low-Resolution Spectroscopy

### 2012-10-16 2012-oss-mrs/ms.tex
Issues #2-4 corrected

The Milky Way stellar halo has partly formed through the accretion of satellites which are disrupted by tidal forces as they fall into the Milky Way's potential. Stars which were once gravitationally bound to the satellite are left behind in a stream of stars. Stream kinematics are sensitive to the shape of the galactic potential, allowing us to constrain the Milky Way potential, and reconstruct the formation history of the Galaxy. The level of accreted substructure in the Milky Way has only recently become apparent through multi-band photometric surveys like the Sloan Digital Sky Survey (SDSS). The more prominent of the detectable substructures, like Sagittarius, have been well-studied. One of the more prominent \--- yet less studied \--- substructures is that of the Orphan Stream.

The Orphan Stream was independently detected by both \citet{Grillmair_Dionatos_2006} and \citet{Belokurov_et-al_2006}, and is distinct from other substructures in the halo. The stream stretches over $60\,^\circ$ in the sky, has a low surface brightness and a narrow stream width of only $\sim$2\,$^\circ$ and as the name suggests, the parent object largely remains a mystery. The stream extends past the celestial equator \--- outside the SDSS footprint \--- but has not been detected in existing southern surveys \citep{Newberg_et-al_2010}. Whilst the parent system remains elusive, significant effort has been placed on associating the stream with known Milky Way satellites \citep{Zucker_et-al_2006, Fellhaur_et-al_2007,Jin_Lynden_Bell_2007,Sales_et-al_2008}. In contrast, there has been relatively limited observational work on the Orphan Stream itself other than the original discovery papers \citep{Grillmair_Dionatos_2006, Belokurov_et-al_2006, Belokurov_et-al_2007} and the work of \citet{Newberg_et-al_2010}. This is largely to be expected given the absence of multi-band photometry in the southern sky and the low total luminosity of the stream, making it difficult to reliably separate Orphan Stream members from halo stars. Further understanding on the extent of the stream awaits the SkyMapper and Pan-STARRS photometric surveys \citep{Keller_et-al_2007, Hodapp_et-al_2004}.

@@

Given our colour selection we expect to recover giants, and dwarf contaminants. The lack of 2MASS photometry for the selected stars means we cannot use the $(J-H, H-K)$ diagram to aid the separation of candidate giants from contaminating dwarfs.

@@

>>>>

The Milky Way stellar halo has partly formed through the accretion of satellites which are disrupted by tidal forces as they fall into the Milky Way's potential. Stars which were once gravitationally bound to the satellite are strewn along the progenitor's orbit in leading and trailing streams of stars. The kinematics of the stream are sensitive to the shape of the galactic potential, allowing us to constrain the Milky Way potential, and reconstruct the formation history of the Galaxy. The level of accreted substructure in the Milky Way has only recently become apparent through multi-band photometric surveys like the Sloan Digital Sky Survey (SDSS). The more prominent of the detectable substructures, like Sagittarius, have been well-studied. One of the more prominent \--- yet less studied \--- substructures is that of the Orphan Stream.

The Orphan Stream was independently detected by both \citet{Grillmair_2006} and \citet{Belokurov_et-al_2006}, and is distinct from other substructures in the halo. The stream stretches over $60\,^\circ$ in the sky, has a low surface brightness and a narrow stream width of only $\sim$2\,$^\circ$ and as the name suggests, the parent object largely remains a mystery. The stream extends past the celestial equator \--- outside the SDSS footprint \--- but has not been detected in existing southern surveys \citep{Newberg_et-al_2010}. Whilst the parent system remains elusive, significant effort has been placed on associating the stream with known Milky Way satellites \citep{Zucker_et-al_2006, Fellhaur_et-al_2007,Jin_Lynden_Bell_2007,Sales_et-al_2008}. In contrast, there has been relatively limited observational work on the Orphan Stream itself other than the original discovery papers \citep{Grillmair_Dionatos_2006, Belokurov_et-al_2006, Belokurov_et-al_2007} and the work of \citet{Newberg_et-al_2010}. This is largely to be expected given the absence of multi-band photometry in the southern sky and the low total luminosity of the stream, making it difficult to reliably separate Orphan Stream members from halo stars. Further understanding on the extent of the stream awaits the SkyMapper and Pan-STARRS photometric surveys \citep{Keller_et-al_2007, Hodapp_et-al_2004}.

@@

Given our colour selection we expect to recover giants and contaminating dwarf contaminants. The lack of 2MASS photometry for the selected stars means we cannot use the $(J-H, H-K)$ diagram to aid the separation of candidate giants from contaminating dwarfs.

@@

\bibitem[{{Grillmair} (2006)}]{Grillmair_2006}
{Grillmair}, C.~J. 2006, \apj, 643, L37
